---
title: "R Notebook"
output: html_notebook
---

## Loading libraries and defining functions
```{r}
##### LIBRARIES #####
list.of.packages <- c("pbmcapply", "foreach", "doParallel")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if (length(new.packages)) install.packages(new.packages)

library(pbmcapply)
library(foreach)
library(doParallel)

##### FUNCTIONS #####

greppend <- function(pattern, 
                     x, 
                     x.col.input = colnames(x),
                     x.col.output = colnames(x)) {
  pb = progressBar(min = 0, max = length(pattern))
  new.table = data.frame()
  for (variable in 1:length(pattern)) {
    pos = grep(pattern = pattern[variable], x = x[, x.col.input])
    new.table = rbind.data.frame(new.table, x[pos, x.col.output])
    setTxtProgressBar(pb, value = variable)
  }
  close(pb)
  return(new.table)
}

```



```{r}
##### OPENING FILES #####

setwd('/share/analysis/hecatos/juantxo/Score/Interactions/')
miRanda.table = read.table(file = 'ALLmRNAtranscripts_vs_ALLmiRNA3.parsed', 
                           stringsAsFactors = F)
setwd("/share/analysis/hecatos/juantxo/score_protein_analysis/UNTR/shift-FALSE")
proteins.table = read.table('./TRC/most_correlated_proteins_trc.tsv')
colnames(miRanda.table)[1:2] = c('miRNA.ID', 'mRNA.ID')
setwd('/share/analysis/hecatos/juantxo/tableomics/')
protrans = read.csv('./uniprot-yourlist_M20190501.csv2', header = T, 
                    stringsAsFactors = F)



```


##GET PROTEIN NAMES TO UNIQUE MRNA NAMES

```{r}


mrnas.unique = as.data.frame(unique(miRanda.table$mRNA.ID))
colnames(mrnas.unique) = 'transcripts'
mrnas.unique$protein = NA

pb = progressBar(min = 0, max = nrow(mrnas.unique))

mrnas.notfound = 0

for (i in 1:nrow(mrnas.unique)) {
  mrna.protrans.pos = grep(pattern = mrnas.unique[i, 1], 
                          x = protrans[, 1])
  if (length(mrna.protrans.pos) > 0) {
    mrnas.unique$protein[i] = protrans$Entry[mrna.protrans.pos]
  } else {
    mrnas.notfound = mrnas.notfound + 1
  }
  if (i == nrow(mrnas.unique)) {
    print(paste('Number of mRNAs not found:', mrnas.notfound))
  }
  setTxtProgressBar(pb, value = i)
}
close(pb)

trc.mrnas.table = greppend(pattern = proteins.table$protlist, 
                           x = mrnas.unique, x.col.input = 'protein')

inter.trc = greppend(pattern = trc.mrnas.table[, 1], 
                     x = miRanda.table, 
                     x.col.input = 'mRNA.ID')

# miRanda.df = as.data.frame(miRanda.table)
# miRanda.df$protein = NA
# 
# 

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
