---
title: "R Notebook"
output: html_notebook
---

## Loading libraries and defining functions
```{r}
##### LIBRARIES #####
list.of.packages <- c("pbmcapply", "foreach", "doParallel")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if (length(new.packages)) install.packages(new.packages)

library(pbmcapply)
library(foreach)
library(doParallel)

##### FUNCTIONS #####

greppend <- function(pattern, 
                     x, 
                     x.col.input = colnames(x),
                     x.col.output = colnames(x)) {
  pb = progressBar(min = 0, max = length(pattern))
  new.table = data.frame()
  for (variable in 1:length(pattern)) {
    pos = grep(pattern = pattern[variable], x = x[, x.col.input])
    new.table = rbind.data.frame(new.table, x[pos, x.col.output])
    setTxtProgressBar(pb, value = variable)
  }
  close(pb)
  return(new.table)
}

```

## Opening files

```{r}
setwd('/share/analysis/hecatos/juantxo/Score/Interactions/')
miRanda.table = read.table(file = 'ALLmRNAtranscripts_vs_ALLmiRNA3.parsed', 
                           stringsAsFactors = F)
setwd("/share/analysis/hecatos/juantxo/score_protein_analysis/UNTR/shift-FALSE")
proteins.table = read.table('./TRC/most_correlated_proteins_trc.tsv')
colnames(miRanda.table)[1:2] = c('miRNA.ID', 'mRNA.ID')
head(miRanda.table)
head(proteins.table)

```
One of the issues of our `proteins.table` is that it only contains 1 out of the 
many transcripts that may translate to the protein of that row. Therefore, we 
will have to look into a solution that might give us the rest of transcripts. 
For that, we require a list with both columns: all transcripts + their proteins. 
We do have one list like that, but its transcripts are frequently joined together in a single string:
```{r}
setwd('/share/analysis/hecatos/juantxo/tableomics/')
protrans = read.csv('./uniprot-yourlist_M20190501.csv2', header = T, 
                    stringsAsFactors = F)
head(protrans[grep(';', protrans[, 1]), ])
```

So first we will need a better mRNA - Protein list, which can be done getting the proteins names out of the transcript names in the miRanda table.

## Get protein names to unique mRNA names  
To make it faster, it's reasonable to only search the counterpart of the transcripts that are unique, especially in a table like miRanda, where 1 transcript can have > 1 interaction:

```{r}
mrnas.unique = as.data.frame(unique(miRanda.table$mRNA.ID))
colnames(mrnas.unique) = 'transcripts'
```

Now we can look for the corresponding proteins of that list:
```{r}
mrnas.unique$protein = NA

pb = progressBar(min = 0, max = nrow(mrnas.unique))

mrnas.notfound = 0

for (i in 1:nrow(mrnas.unique)) {
  mrna.protrans.pos = grep(pattern = mrnas.unique[i, 1], 
                          x = protrans[, 1])
  if (length(mrna.protrans.pos) > 0) {
    mrnas.unique$protein[i] = protrans$Entry[mrna.protrans.pos]
  } else {
    mrnas.notfound = mrnas.notfound + 1
  }
  if (i == nrow(mrnas.unique)) {
    print(paste('Number of mRNAs not found:', mrnas.notfound))
  }
  setTxtProgressBar(pb, value = i)
}
close(pb)
```

Having the transcript-protein table, we can now look for a list of all the transcripts related to our set of proteins
```{r}
trc.mrnas.table = greppend(pattern = proteins.table$protlist, 
                           x = mrnas.unique, x.col.input = 'protein')
```

Finally, we look for the interactions of those transcripts in the miRanda file
```{r}
inter.trc = greppend(pattern = trc.mrnas.table[, 1], 
                     x = miRanda.table, 
                     x.col.input = 'mRNA.ID')

```

